PanGraph: scalable bacterial pan-genome graph construction \\ Supplementary Information

### 2022-09-23 supplementary.tex
feat: added updated supplementary table
feat: improved kmer figure
feat: improved projection figures

@@

\begin{figure}[htb]
    \includegraphics[width=.8\textwidth]{figs_suppl/proj_fig.pdf}
    \caption{{\bf Marginalized graphs are compatible with pairwise graphs}. Comparison of marginalized (MG) and pairwise (PW) built graphs for 5 different species. For each pair of strains we measure the length of segments in which MG and PW graphs agree on whether the segments are shared on both strains (\textit{agree on sharing}). These can either be both shared (\textit{shared on both}) or both private (\textit{private on both}). We also measure the length of segments on which the MG and PW graphs disagree (\textit{disagree on sharing}). For each of these for cases we report the total length as fraction of the average genome (left column) and the average size of each segment (right column). For each category we display the distribution of average results for 50 different pairs (45 for PM).
    }
    \label{fig:marginalize-suppl}
\end{figure}

>>>>

\begin{table}[hb]
    \setlength{\tabcolsep}{9pt}
    \begin{tabular}{lccccc}
        \hline\hline
        Species         & N. isolates & $\avg{L_\text{gen}}$ [Mbp] & $L_\text{pang}$ [Mbp] & $L_\text{core}$ [Mbp] & $\avg{d_\text{core}}$ \\
        \hline
        E.~Coli         & 307         & 5.0                        & 17.7                  & 0.7                   & 1.6\%                 \\
        K.~Pneumoniae   & 109         & 5.3                        & 13.0                  & 2.3                   & 0.8\%                 \\
        H.~Pylori       & 85          & 1.6                        & 1.9                   & 0.6                   & 4.2\%                 \\
        M.~Tuberculosis & 51          & 4.4                        & 4.1                   & 2.4                   & 0.03\%                \\
        P.~Marinus      & 10          & 1.8                        & 3.3                   & 0.7                   & 26.9\%                \\
        \hline
    \end{tabular}
    \caption{{\bf Dataset overview}. We downloaded complete chromosome sequences from RefSeq for 5 different bacterial species. For each species we report the number of isolates downloaded, along with the average chromosome length $\avg{l}$, total size of pangenome  $L_\text{tot}$ and core genome $L_\text{core}$, and average pairwise divergence on core genes $\avg{d}$.}
    \label{table:panx-dataset-updated}
\end{table}

@@

\begin{figure}[htb]
    \includegraphics[width=.9\textwidth]{figs_suppl/proj_fig.pdf}
    \caption{{\bf Marginalized graphs are compatible with pairwise graphs}. Comparison of marginalized (MG) and pairwise (PW) built graphs for 5 different species. For each pair of strains we measure the length of segments in which MG and PW graphs agree on whether the segments are shared on both strains (\textit{agree on sharing}). These can either be both shared (\textit{shared on both}) or both private (\textit{private on both}). We also measure the length of segments on which the MG and PW graphs disagree (\textit{disagree on sharing}). For each of these for cases we report the total length as fraction of the average genome (left column) and the average size of each segment (right column). For each category we display the distribution of average results for 50 different pairs (45 for PM).
    }
    \label{fig:marginalize-suppl}
\end{figure}
